Modeling the near-wake of a vertical-axis cross-flow turbine with 2-D and 3-D RANS

### 2015-09-14 paper.tex
Remove basically empty validation section; content in results
Simulation time --> simulated time

\section{Model validation}

Models were validated against several open datasets.

@@

Computations for the 3-D cases were run on 192 processes and took on the order
of 1,000 CPU hours per second of simulation time. The 2-D simulations were run
on a single processor and took on the order of one CPU hour per second.

>>>>

@@

Computations for the 3-D cases were run on 192 processes and took on the order
of 1,000 CPU hours per second of simulated time. The 2-D simulations were run on
a single processor and took on the order of one CPU hour per second.
